Classless Java: Tuning Java Interfaces

### 2015-12-06 paper/sections/Implementation.tex
review 6 (boh, is ok? non convincing but I do not know what to improve) and exp problem
More discussion on language tuning in section 6, plus CoFoJa

Our implementation is based on an extension of Lombok. The Lombok
project~\cite{lombok} is a Java tool that aims at removing (or
reducing) Java boilerplate code via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST for the 
annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.

@@

>>>>

Our implementation is based on an extension of Lombok. The Lombok
project~\cite{lombok} is a Java library that aims at removing (or
reducing) Java boilerplate code via
annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString}
methods, respectively.  Furthermore, Lombok provides a number of
interfaces for users to create custom transformations, as extensions
to the original framework.
A transformation is based on a handler, which acts on the AST for the 
annotated node and returns a modified AST for analysis and
generation afterwards. Such a handler can either be a Javac handler or
an Eclipse handler.

@@

\paragraph{Lombok do Language tuning}
We consider Lombock to be the most developed example of language tuning; while they do not introduce a specific term for what they are doing,
their slogan \emph{``Spice up your java''} seams to be in line with the philosophy of language tuning.
Some other example of language tuning in Lombok include the \Q@val@ type, similar to \Q@auto@ in C\# or C++04.
Another library doing language tuning is CoFoJa~\cite{}, where annotations are used to insert pre-post conditions in generated bytecode.
